\chapter*{Bibliografía.}
\begin{itemize}
\item[[1]] Lewis Ryder ;\textit{Introduction to General Relativity.};Cambridge University Press (2009).
\item[[2]] Steven Weinberg ;\textit{The Quantum Theory of Fields, Volume I-II.};Cambridge University Press (1995).
\item[[3]] Daniel Baumann;\textit{TASI Lectures on Inflation.};\texttt{https://arxiv.org/pdf/0907.5424v2.pdf}.
\item[[4]] C. Cohen-Tannudji, B. Diu ;\textit{Quantum Mechanics, Volume One}; Wiley, New-York, (1991).
\item[[5]] Mathieu Beau; \textit{Feynman Integral and one/two slits electrons diffraction : an analytic study}; \texttt{arXiv:1110.2346v3}.
\item[[6]]  L.D. Faddeev,  V.N. Popov ;\textit{Feynman diagrams for the Yang-Mills field}; Physics Letters B Volume 25, Issue 1, 24 July 1967, Pages 29-30.
\item[[7]] Lewis H. Ryder;\textit{Quantum Field Theory};Second Edition (1996) 
\item[[8]] M Nakahara;\textit{Geometry, Topology and Physics};Second Edition (2003) 
\item[[9]]  C.N Yang,  R.L Mills ;\textit{Conservation of Isotopic Spin and Isotopic Gauge Invariance}; Phys. Rev. 96, 191 – Published 1 October 1954.
\item[[10]]  Hermann Weyl;\textit{Elektron und Gravitation. I}; Zeitschrift für Physik, May 1929, Volume 56, Issue 5, pp 330-352.
\item[[11]] R.M. Wald.;\textit{General Relativity.};University of Chicago Press, (1984). 
\item[[12]]  Bryce DeWitt;\textit{Dynamical Theory in Curved Spaces. I. A Review of the Classical and Quantum Action Principles.}; Reviews of Modern Physics, July 1957 .
\item[[13]]  Christian Grosche;\textit{An introduction into the Feynman path integral.}; arXiv:hep-th/9302097v1 20 Feb 1993 .
\item[[14]]   Duru and H. Kleinert;\textit{Solution of the Path Integral for the H-Atom.}; Phys. Letters B 84, 185 (1979).
\item[[15]]   Duru and H. Kleinert;\textit{Quantum Mechanics of H-Atom from Path Integrals.};  Fortschr. d. Phys. 30, 401 (1982).
\item[[16]]  Hagen Kleinert;\textit{Path Integrals in Quantum Mechanics, Statistics, Polymer Physics, and Financial Markets.};  World Scientific, Singapore 2009.
\item[[17]]  M Chaichian and A Demichev;\textit{Path Integrals in Physics, Volume I
Stochastic Processes and Quantum Mechanics.};  IOP Publishing Ltd 2001.
\item[[18]] Dennis V. Perepelitsa;\textit{Path Integrals in Quantum Mechanics.};\texttt{http://goo.gl/y29SeM}.
\item[[19]] Sagnac, Georges;\textit{L'éther lumineux démontré par l'effet du vent relatif d'éther dans un interféromètre en rotation uniforme.}; Comptes Rendus 157: 708–710.
\item[[20]] Sagnac, Georges;\textit{Sur la preuve de la réalité de l'éther lumineux par l'expérience de l'interférographe tournant.};  Comptes Rendus 157: 1410–1413.
\item[[21]] Guido Rizzi, Matteo Luca Ruggiero ;\textit{Path Integrals in Quantum Mechanics.};Springer Science+Business Media Dordrecht (2004).
\item [[22]] Christopher C. Bernido and Glenn Aguarte; \textit{Summation over histories for a particle in spherical orbit around a black hole.};  Physical Review D, Volume 56, Number 4, (1997).
\item[[23]] Hector Alzate ;\textit{Física de las ondas.}; Univerisad de Antioquia (2007).
\end{itemize}
